Parsing Postfix log files

### 2009-03-31 doc/logparser-implementation.tex
Changes from proofreading of introduction chapter.
Added a new action, DELIVERY_ERROR, to save data from delivery errors that     happen before a disconnection. Changed some UNINTERESTING rules to use DELIVERY_ERROR and SAVE_DATA. Removed connection_data fields from UNINTERESTING rules. Added a debug field to rules, so that individual rules can have debugging     information dumped when they recognise a log line. Improved the abstract, though it still needs work. Documented everything in the thesis.

\showgraph{build/logparser-flow-chart-part-1}{Parser flow chart}{flow chart
image}

@@

@@

    \item The regex from the recognising rule and the log line it
        recognised can be printed, so that the user can verify that the
        correct rule recognised each log line.  A possible variant of this
        would be to mark specific rules so only their regexes and the log
        lines they recognise would be printed.

@@

\subsection{Actions in the \parsernamelong{}}

@@

@@

    \caption{Example rule}
    \empty{}\label{Example rule in implementation table}
    \begin{tabular}{ll}

    \textbf{Field}      & \textbf{Value}                                    \\
    name                & Unknown sender domain                             \\
    description         & We do not accept mail from unknown domains        \\
    restriction\_name   & reject\_unknown\_sender\_domain                   \\
    program             & \daemon{smtpd}                                    \\
    regex               & \verb!^__RESTRICTION_START__ <(__SENDER__)>: !    \\
                        & \verb!Sender address rejected: Domain not found;! \\
                        & \verb!from=<\k<sender>> to=<(__RECIPIENT__)> !    \\
                        & \verb!proto=E?SMTP helo=<(__HELO__)>$!            \\
    result\_data        &                                                   \\
    connection\_data    &                                                   \\
    action              & \action{DELIVERY\_REJECTED}                       \\
    hits                & 0                                                 \\
    hits\_total         & 0                                                 \\
    priority            & 0                                                 \\
    %cluster\_group      & 400                                               \\

@@

@@

\section{Limitations and Possible Improvements}

>>>>

\showgraph{build/logparser-flow-chart-part-1}{\parsernamelong{} flow
chart}{flow chart image}

@@

    \item [debug] If this field is true, a warning will be issued with
        information about the rule and the log line every time this rule
        recognises a log line.  This field is optional.

@@

    \item The regex from the recognising rule and the log line it
        recognised can be printed, so that the user can verify that the
        correct rule recognised each log line.  Individual rules can also
        set their debug field to true, and debugging information will be
        printed each time they recognise a log line.

@@

\subsection{Actions In The \parsernamelong{}}

@@

    \item [DELIVERY\_ERROR] Process log lines indicating that an error
        occurred and the remote client disconnected; the log lines
        processed by this action will be followed by log lines processed by
        the \action{DISCONNECT} action, so all this action does is save
        data from the log line.

@@

    \caption{Example of a rule used by \parsernameshort{}}
    \empty{}\label{Example rule in implementation table}
    \begin{tabular}{ll}

    \textbf{Field}      & \textbf{Value}                                    \\
    name                & Unknown sender domain                             \\
    description         & We do not accept mail from unknown domains        \\
    restriction\_name   & reject\_unknown\_sender\_domain                   \\
    program             & \daemon{smtpd}                                    \\
    regex               & \verb!^__RESTRICTION_START__ <(__SENDER__)>: !    \\
                        & \verb!Sender address rejected: Domain not found;! \\
                        & \verb!from=<\k<sender>> to=<(__RECIPIENT__)> !    \\
                        & \verb!proto=E?SMTP helo=<(__HELO__)>$!            \\
    result\_data        &                                                   \\
    connection\_data    &                                                   \\
    action              & \action{DELIVERY\_REJECTED}                       \\
    hits                & 0                                                 \\
    hits\_total         & 0                                                 \\
    priority            & 0                                                 \\
    debug               & 0                                                 \\
    %cluster\_group      & 400                                               \\

@@

    \item [debug] controls the debugging information that can be generated
        when this rule recognises a log line.

@@

\section{Limitations And Possible Improvements}

### 2009-03-31 doc/logparser.tex
Added a new action, DELIVERY_ERROR, to save data from delivery errors that     happen before a disconnection. Changed some UNINTERESTING rules to use DELIVERY_ERROR and SAVE_DATA. Removed connection_data fields from UNINTERESTING rules. Added a debug field to rules, so that individual rules can have debugging     information dumped when they recognise a log line. Improved the abstract, though it still needs work. Documented everything in the thesis.

\newcommand{\numberOFactions}[0]{%
    22%
}

@@

    Parsing Postfix log files is much more difficult than it first appears,
    but it \textit{is\/} possible to achieve a high degree of accuracy in
    understanding the log files and reconstructing the actions taken by
    Postfix to generate the log files.  This paper describes the creation
    of a parser for Postfix log files, documenting the architecture
    developed and the parser implementing it, explaining the difficulties
    encountered and the solutions developed, with reference to an
    implementation that stores data gleaned from the log files in an SQL
    database.  The gathered data can then be used to optimise current
    anti-spam measures, provide a baseline to test new anti-spam measures
    against, or to produce statistics showing how effective those measures
    are.

    XXX ABSTRACT FROM SGAI PAPER\@.

    Some parsers need to be very precise and strict when parsing, yet must
    allow users to easily adapt or extend the parser to parse new inputs,
    without requiring that the user have an in-depth knowledge and
    understanding of the parser's internal workings.  This paper presents a
    novel parsing architecture, designed for parsing Postfix log files,
    that aims to make the process of parsing new inputs as simple as
    possible, enabling users to trivially add new rules (to parse variants
    of existing inputs) and relatively easily add new actions (to process a
    previously unknown category of input).  The architecture scales
    linearly or better as the number of rules and size of input increases,
    making it suitable for parsing large corpora or months of accumulated
    data.

@@

    XXX CHECK ALL ``UNINTERESTING'' RULES TO SEE IF THEY COULD BE USED\@.

@@

>>>>

\newcommand{\numberOFactions}[0]{%
    23%
}

@@

    Parsing Postfix log files is much more difficult than it first appears,
    but it \textit{is\/} possible to achieve a high degree of accuracy in
    understanding Postfix log files and reconstructing the actions taken by
    Postfix that generated the log files.  This thesis describes the
    creation of a parser for Postfix log files, documenting the
    architecture developed and the parser implementing it, explaining the
    difficulties encountered and the solutions developed, with reference to
    an implementation that stores data gleaned from the log files in an SQL
    database.  The gathered data can be used to optimise current anti-spam
    measures, to produce statistics showing how effective those measures
    are, or to provide a baseline to test new anti-spam measures against.
    The Postfix log file parser needs to be very precise and strict when
    parsing, yet must allow users to easily adapt or extend it to parse new
    inputs, without requiring that the user have an in-depth knowledge and
    understanding of the parser's internal workings.  The newly developed
    architecture aims to make the process of parsing new inputs as simple
    as possible, enabling users to trivially add new rules (to parse
    variants of existing inputs) and relatively easily add new actions (to
    process a previously unknown category of inputs).  The architecture
    scales linearly or better as the number of rules and size of input
    increases, making it suitable for parsing large corpora or months of
    accumulated data.

@@

@@

    XXX RUN ``test-some'' AGAIN TO UPDATE THE DB\@.
